Paraphrasing for Style

### 2012-09-01 paper/paper.tex
minor changes
Changed the title, added to the conclusions, and incorporated some of bill's changes to the abstract

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We show that even with a relatively small amount of parallel training data available, it is
possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
baselines based on dictionaries and out-of-domain parallel text.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|r|}
    \hline
    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 & 0.31 \\
    \hline
    dissimilarity & PINC & 0.78 & 0.82 \\
    \hline
    style & BLEU & 0.07 & 0.06 \\
    \hline
    style & PINC & 0.20 & 0.45 \\
    \hline
    style & Cosine & 0.37 & 0.41 \\
    \hline
    style & LM & 0.45 & 0.48 \\
    \hline
    style & Logistic regression & 0.47 & 0.48 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
  between the automatic metrics and human judgements from each annotator.}
  \label{correlation}
\end{table}

@@

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.

>>>>

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\title{Paraphrasing for Style}
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We show that even with a relatively small amount of parallel training data, it is
possible to learn paraphrase models which capture stylistic phenomena, and these models outperform
baselines based on dictionaries and out-of-domain parallel text.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|r|}
    \hline
    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 & 0.31 \\
    \hline
    dissimilarity & PINC & 0.78 & 0.82 \\
    \hline
    style & BLEU & 0.07 & 0.06 \\
    \hline
    style & PINC & 0.20 & 0.45 \\
    \hline
    style & Cosine & 0.37 & 0.41 \\
    \hline
    style & LM & 0.45 & 0.48 \\
    \hline
    style & Logistic regression & 0.47 & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
  between the automatic metrics and human judgements from each annotator.}
  \label{correlation}
\end{table}

@@

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.

We have shown that access to even a small amount of parallel text produces paraphrase systems 
capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
Our paraphrase systems targeting Shakesperean English could be benefical for educational applications, for example helping to
make Shakespeare's work accessable to a broader audience.
Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or
translating legal documents into nontechnical English. 
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.
